Finch: Sparse and Structured Array Programming with Control Flow

### 2024-04-05 sections/intro.tex
Update on Overleaf.

\textbf{In this work, we propose a new programming language, Finch, which supports \textit{both} flexible control flow and diverse data structures.}
%
Finch facilitates a programming model which resolves the challenges of computing over structured arrays by \textbf{combining control flow and data structures into a common representation where they can be co-optimized}.
%
In particular, Finch automatically specializes the control flow to the data so that performance engineers can focus on experimenting with many algorithms.
%
Finch supports a familiar programming language of loops, statements, if conditions, breaks, etc, over a wide variety of array structures, such as sparsity, run-length-encoding, symmetry, triangles, padding, or blocks. 
%
This support would be useless without the appropriate level of structural specialization; Finch reliably utilizes the key properties of structure, such as structural zeros, repeated values, or clustered non-zeros.
%

>>>>

\textbf{In this work, we propose a new programming language, Finch, which supports \textit{both} flexible control flow and diverse data structures.}
%
Finch facilitates a programming model which resolves the challenges of computing over structured arrays by \textbf{combining control flow and data structures into a common representation where they can be co-optimized}.
%
In particular, Finch automatically specializes the control flow to the data so that performance engineers can focus on experimenting with many algorithms.
%
Finch supports a familiar programming language of loops, statements, if conditions, breaks, etc., over a wide variety of array structures, such as sparsity, run-length-encoding, symmetry, triangles, padding, or blocks. 
%
This support would be useless without the appropriate level of structural specialization; Finch reliably utilizes the key properties of structure, such as structural zeros, repeated values, or clustered non-zeros.
%
